Followers Are Not Enough: Beyond Structural Communities in Online Social Networks \\Followers Are Not Enough: A Question-Oriented Approach to Community Detection

### 2014-07-30 paper-for_arxiv/results.tex

Another interesting example is a community whose topics tend to focus on Denver and Colorado. These users do not belong to the same community in the interaction-based network, but most of them do belong to the same community in the activity-based network. This indicates that these users react to the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities. As expected, among the most influential users (in terms of transfer entropy) we find \@Colorado, which is the state official Twitter account, \@ConnectColorado, a page created to connect Coloradans, and CBS Denver account.

Lastly, it is interesting to note that in the top ten most influential users (ranked using the total outgoing strength in the activity-based network) we find two users (Ann Tran and Jessica Northey) that were listed by Forbes in the ``Top 10 Social Media Influencers".

>>>>

Another interesting example is a community whose topics tend to focus on Denver and Colorado. These users do not belong to the same community in the interaction-based network, but most of them do belong to the same community in the activity-based network. This indicates that these users react to the same events and issues regarding Colorado and are therefore strongly connected in the topic-based and activity-based networks, but at the same time they do not directly interact with each other and are therefore more loosely connected in the interaction-based networks, where they belong to different communities.

As an aside, it is interesting to examine who the most influential users are in these communities, as determined by transfer entropy. Recall that influence in this context refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee. Said differently, higher transfer entropy, or a higher reduction in uncertainty, implies more influence. Interestingly, among the most influential users in these communities, those with highest transfer entropy on average, we find \@Colorado, which is the state official Twitter account, \@ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency. This means that these accounts had high influence in terms of their followers activity on Twitter. This is not surprising as these communities discuss Colorado and these accounts provide information on this topic. However, this does provide a nice sanity check that this measure of activity based influence makes sense and suggests this could be a nice measure for influence on social media if used with other measures. This is discussed more in future work.

Lastly, it is interesting to note that two of the Forbes ``Top 10 Social Media Influencers", % ranked using the total outgoing strength in the activity-based network, 
 happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as highly influential.% members, as categorized by transfer entropy. 
 This does not prove, but suggests that this measure of activity-based or information-theoretic influence may be useful in finding influential members purely based on their temporal tweet history while completely ignoring both tweet content and social class.
